Modalities for Virtualizing Memory Addresses

### 2022-12-02 intro.tex
some points on intro

We develop these ideas in an Iris-based\mytodo{cite JFP} separation logic, and verify simplified versions of several critical virtual-memory-related pieces of OS functionality, including mapping and unmapping pages, and describing the self-referential identity maps used in most kernels to allow convenient access to physical memory.

>>>>

We develop these ideas in an Iris-based\mytodo{cite JFP} separation logic, and verify simplified versions of several critical virtual-memory-related pieces of OS functionality, including mapping and unmapping pages, and describing the self-referential identity maps used in most kernels to allow convenient access to physical memory. Our contributions are:
\begin{itemize}
\item We present the first Separatoin Logic for reasoning about address-space management including mapping and unmapping pages, and describing the self-referential identity maps used in most kernels to allow convenient access to physical memory 
\item We develop a novel high-level modal abstraction for address-space management which allows us to assert certain facts whose validity are indexed by the address of a certain address-space.
\item We define logical relations, such as introduction and elimination, to capture the logical facts about address-space operations, e.g. context-switch
\item We discuss how our methodology is a high-level, light-weight mechanism that differ from defining contingent truth as predicate qualifier, e.g. \textit{Stackable} ~\cite{}, and build a mechanism, a custom-tailored weakest-precondition, to operated on these certain type predicates.  
 \end{itemize}
